Miniproject - Elliptic Curves

### 2022-03-16 Elliptic Curves/submission.tex
Almost done with 3(i)

    So it is left to show that $\beta/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
\end{proof}
\end{document}

>>>>

    So it is left to show that $\beta_2/(2\beta^2)$ has a third root in $\Q$ and that $u^2 \alpha_2 = -v$.
    First, note that $u^2 \alpha_2 = -v$ is equivalent to $u^6 \alpha_2 = -v^3$ (since there is only one cubic root in $\Q$).
    Have
    \begin{equation*}
        u^4 \alpha_2 = -v^3 \ \Leftrightarrow \ \frac {\beta_2^2} {4\beta^4} \alpha_2^3 = -\frac {\beta_2^3} {\beta^3} \ \Leftrightarrow \ \alpha_2^3 = -4 \beta \beta_2
    \end{equation*}
    Consider the following SAGE script:
    \lstinputlisting[language = python]{./3i_algebra.sage}
    The output shows that $\alpha_2^3 = -4 \beta \beta_2$ already follows from the facts
    \begin{align*}
        &(0, \beta) \in E, \\
        &(\alpha_2, \beta_2) \in E, \\
        &[2](0, \beta) = (\alpha_2, \beta_2), \\
        &[2](\alpha_2, \beta_2) = (0, -\beta)
    \end{align*}
    Hence it suffices to show that $\beta_2/(2\beta^2)$ has a third root in $\Q$.
\end{proof}
\end{document}
